\documentclass[12pt,a4paper]{report}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[top=2.5cm,bottom=2.5cm,left=3cm,right=3cm]{geometry}
\usepackage{titlesec}
\usepackage{lipsum}
\usepackage{float}

% Format
\pagestyle{fancy}
\fancyhf{}
\rhead{ELEC40006: EEESeaBoat}
\lhead{Group 14 Report}
\cfoot{\thepage}

% Title page
\title{\textbf{EEESeaBoat Project Report} \\ \large ELEC40006 -- Electronics Design Project 1}
\author{
\textbf{Group 14:} \\ David Lesman (CID: 02371181) \\ Thanus Palakumar (CID: 02556047) \\ Denzil Erza-Essien (CID: 02593040) \\ Lukas Mykhnenko (CID: 02579708) \\ \\ \\
\textbf{Word Count:} 9,228
}
\date{May/June 2025}

\begin{document}

\maketitle
\tableofcontents
\newpage

\chapter{Abstract}
\input{subpages/abstract.tex}

\chapter{Introduction and Targeted Objectives}
\input{subpages/intro.tex}
\chapter{Project Management and Team Coordination}
\input{subpages/management.tex}

% Placeholder for next chapters
\chapter{Infrared Detection}
\input{subpages/infrared.tex}

\chapter{Ultrasound Detection}
\input{subpages/ultrasound.tex}

\chapter{Radio Detection}
\input{subpages/radio.tex}

\chapter{Magnetic Detection}
\input{subpages/magnetism.tex}

\chapter{Arduino and CAD Integration}
\input{subpages/arduino.tex}

\chapter{Conclusion}
\input{subpages/conclusion.tex}

\chapter{Project Evaluation and Future Actions}
\input{subpages/evaluation.tex}

\appendix
\chapter{References}
\begin{enumerate}
    \item Cadence PCB Solutions, 2024. \textit{Non-inverting Op-Amp: Explanation and Applications}. [Online]
          Available at: \url{https://resources.pcb.cadence.com/blog/2024-non-inverting-op-amp-explanation-and-applications}
          [Accessed 15 May 2025].

    \item Chaparro, L. F., 2011. \textit{Continuous-Time Systems}. In: L. F. Chaparro, ed. \textit{Signals and Systems using MATLAB}. Pittsburgh (Pennsylvania): University of Pittsburgh, pp. 117--164.

    \item Electronics Tutorials, 2025. \textit{Op-amp Comparator}. [Online]
          Available at: \url{https://www.electronics-tutorials.ws/opamp/op-amp-comparator.html}
          [Accessed 16 May 2025].

    \item Elena, 2025. \textit{An Overview of the 1N4148 Diode – Pinout, Characteristics, and Applications}. [Online]
          Available at: \url{https://electroniccomponent.com/an-overview-of-the-1n4148-diode-pinout-characteristics-and-applications/}
          [Accessed 15 May 2025].

    \item Farnell, 2018. \textit{Ultrasonic Transducer}. [Online]
          Available at: \url{https://www.farnell.com/datasheets/2647527.pdf}
          [Accessed 15 May 2025].

    \item Fernandez, A., 2025. \textit{Piezoelectric transducers}. [Online]
          Available at: \url{https://power-mi.com/content/piezoelectric-transducers}
          [Accessed 15 May 2025].

    \item Merdan, H., 2025. \textit{Technical Hints}. [Online]
          Available at: \url{https://github.com/hakanmerdan/EEESeaBoat2025/blob/main/doc/README.md}
          [Accessed 13 May 2025].

    \item Microchip, 2017. \textit{MCP6021/1R/2/3/4 Datasheet}. [Online]
          Available at: \url{https://ww1.microchip.com/downloads/en/devicedoc/20001685e.pdf}
          [Accessed 16 May 2025].

    \item Microchip, 2020. \textit{MCP6561/1R/1U/2/4 Comparator Datasheet}. [Online]
          Available at: \url{https://ww1.microchip.com/downloads/en/DeviceDoc/MCP6561-1R-1U-2-4-1.8V-Low-Power-Push-Pull-Output-Comparator-DS20002139E.pdf}
          [Accessed 16 May 2025].

    \item MPE, 2024. \textit{Advantages and disadvantages of surface mount technology}. [Online]
          Available at: \url{https://www.mpe-electronics.co.uk/2024/10/22/advantages-and-disadvantages-of-surface-mount-technology}
          [Accessed 16 May 2025].

    \item Murata, 2025. \textit{AMR Sensors (Magnetic Sensors) FAQ}. [Online]
          Available at: \url{https://www.murata.com/en-eu/support/faqs/sensor/amr/cct/0006}
          [Accessed 16 May 2025].

    \item Se-yuen, M., 2003. \textit{Wave experiments using low-cost 40kHz ultrasonic transducers}. [Online]
          Available at: \url{http://users.df.uba.ar/sgil/physics_paper_doc/papers_phys/mak.pdf}
          [Accessed 15 May 2025].

    \item Spiceman, 2022. \textit{Op-Amp Non-inverting Amplifier Circuit}. [Online]
          Available at: \url{https://spiceman.net/non-inverting-amplifier-circuit/}

    \item Lesman, D., 2025. \textit{EE Design Project GitHub Repository}. [Online]
          Available at: \url{https://github.com/davidlesman/EE-Design-Project}
          [Accessed 11 June 2025].

    \item Khoih, M., 2025. \textit{WiFiWebServer Library}. [Online]
          Available at: \url{https://github.com/khoih-prog/WiFiWebServer}
          [Accessed 11 June 2025].

\end{enumerate}


\end{document}
