\begin{enumerate}
    \item Ultrasound -- Optimising the gain in the circuit when receiving the ultrasonic signal, allowing for detection at a further range.
    \item Arduino -- Should send separate messages to interface with display text and information for duck detection, instead of extracting information from the original text response.
    \item CAD -- Designs had to be redone due to strain from weight (such as magnetic arm), something that should've been considered beforehand.
    \item Radio -- Could have trialled the coil antenna and collected results to compare it against the inductor to see how different the two methods were.
    \item Infrared -- With better time management, a thorough investigation would have built the bandpass filters as well and tested for efficiency by comparing the analogue and digital methods. The phototransistor taken was from the EEBug, but perhaps the remaining 17\% of the budget could have been contributed towards purchasing a more powerful or sensitive phototransistor to ensure clearer signals and smoother detection.
    \item Magnetic --     Could have benefited from a dynamic gain amplification stage. Instead of a fixed gain, an adaptive gain control system would allow the amplifier to automatically adjust its amplification based on the detected magnetic field strength. This would optimize sensitivity for weak, distant signals while preventing saturation from strong, close-range signals, maximizing the effective detection range.
    \item Budgeting -- The cumulative budget came out to £50, but this could have been avoided through better op-amp research (see Table~\ref{tab:component_orders}).
\end{enumerate}

\begin{table}[H]
    \centering
    \small
    \makebox[\textwidth]{%
        \begin{tabular}{|p{5cm}|l|r|r|r|}
            \hline
            \textbf{Description}                   & \textbf{Unit Price (£)} & \textbf{Quantity} & \textbf{Line Sum (£)} \\
            \hline
            MCUSD16A40S12RO Ultrasonic transceiver & 1.76                    & 1                 & 1.76                  \\
            1N4148 Diode                           & 0.04                    & 5                 & 0.20                  \\
            MCP6021-I/P Opamp                      & 1.34                    & 2                 & 2.68                  \\
            DRV5053OAQLPG Hall Effect Sensor       & 0.65                    & 1                 & 0.65                  \\
            LM358N/NOPB Opamp                      & 0.66                    & 1                 & 0.66                  \\
            LM6142BIN/NOPB Opamp                   & 6.94                    & 3                 & 20.82                 \\
            OPA703PA Opamp                         & 4.73                    & 5                 & 23.65                 \\
            LM324N Opamp                           & 0.28                    & 1                 & 0.28                  \\
            \hline
        \end{tabular}
    }
    \caption{Component Orders and Costs}
    \label{tab:component_orders}
\end{table}


